Learning and comparing functional connectomes across subjects

### 2012-12-31 paper.tex
prediction modeling more

\cite{craddock2009}
craddock 2009, Dosenbach 2010, lord 2011, deshpande,

1. importance of interpretation!
2. the need for feature extraction
3. the need for feature selection
4. setting parameters.
5. different methods have different interpretations

% Define predictive modeling and give examples

@@

Predictive models are validated using one or more iterations of cross
validation, which involves training and testing phases.  A cross validation
cycle begins by seperating the available data into two independent subsets:
training data and testing data.  Training involves learning a predictive model
from the training data. During testing the model is applied to the testing data
to predict corresponding values of the target variable.  Prediction accuracy is
then assessed by comparing these predictions to the observed values of the
target variable. In order to make

>>>>

\cite{craddock2009}
% Define predictive modeling and give examples

@@

The quality of a predictive model is determined by its ability to make accurate predictions
from never-before-seen data. This generalization ability is estimated by seperating the 
available data into independet training and testing subsets. A predictive model is learned
from the training data and applied to the testing data to predict corresponding values of the
target variable. Prediction accuracy is then assessed by comparing these predictions to the 
observed value of the target variable. This procedure can be iterated several times for different
splits of the data and averaged to form a single measure of prediction accuracy, in a procedure termed 
cross validation. One of the most important parameters for cross validation is the manner in which data 
are subdivided. There are several strategies for constructing the training dataset ranging from using
all but one observations (leave-one-out cross-validation), using a fraction of the observations
(k-fold cross validation; kfcv), to resampling the observations with replacement (boostrap 
cross-validation, bscv). Although loocv has been popular in neuroimaging applications of MVPA since
it incorporates the largest amount of data into training performs the largest amount of data as it is
easy to implement and results in the same error estimate, its estimates are more variable than 
kfcv or bscv. Split-half cross validation (two-fold cross validation, 2fcv), minimizes the estimation
variance, at the cost of using less training

single observation (leave-one-out cross-validation; loocv), a fraction of the observations (k-fold cross-validation; kfcv),
or resampling the observations with replacement (bootstrap cross-validation; bscv);

, leaving a  A commmon practice is leave-on-out cross-validation (loocv) in which a single observation
is used for testing at each iteration,

is estimated through a one or
more iterations of cross validation.

A cross validation cycle begins by seperating the 
available data into two independent subsets: training data and testing data. A predictive model 
is learned from the training data and subsequently applied to the testing data to predict 
corresponding values of the target variable. Prediction accuracy is then assessed by comparing
these predictions to the observed value of the target variable. This procedure is typically repeated
for several different splits of the data. The simplest is hold-out validation in which the data
is split into testing and training

	One of the most important parameters for cross validation
is the manner in which data are subdivided, which sets the balance between maximally use of the
data for training.

	Cross-validation can be performed
in a variaty of ways, and if performed correctly will result in an unbiased estimator of 
generalization ability. A major choice

Predictive models are validated using one or more iterations of cross
validation, which involves training and testing phases.  A cross validation
cycle begins by seperating the available data into two independent subsets:
training data and testing data.  Training involves learning a predictive model
from the training data. During testing the model is applied to the testing data
to predict corresponding values of the target variable.  Prediction accuracy is
then assessed by comparing these predictions to the observed values of the
target variable.
